### 2016-01-23 project/paper/appendices/sparql.tex
Byzantine errors

\begin{enumerate}
\item \textbf{Links are not broken but queries on them don't work}\\
Take for example the following person Paul Rübig. There is an data item about him on DBpedia:  \url{http://dbpedia.org/page/Paul\_ R\"ubig}. But if you query this specific resource with the query in listing \ref{lst:dbpedia} you will not get any results.
\lstinputlisting[language=SQL, caption=Query that doesn't work, label={lst:dbpedia}]{dbpedia.rq}
\end{enumerate}

>>>>

\begin{enumerate}
\item \textbf{Links are not broken but queries on them don't work}\\
Take for example the following person Paul Rübig. There is an data item about him on DBpedia:  \url{http://dbpedia.org/page/Paul\_ R\"ubig}. But if you query this specific resource with the query in listing \ref{lst:dbpedia} you will not get any results.
\lstinputlisting[language=SQL, caption=Query that doesn't work, label={lst:dbpedia}]{queries/dbpedia.rq}

\item \textbf{\texttt{dati.camera.it} doesn't work at all}\\
In the ToE database there are lot of reference to the Italian linked open data source \texttt{dati.camera.it}. Unfortunately none of our queries seem to give any result. Even not for a really simple one, as you can see in listing \ref{lst:dati}. Even though it's link \url{http://dati.camera.it/ocd/persona.rdf/p35360} seems to work fine.

\lstinputlisting[language=SQL, caption=Query that doesn't work on \texttt{dati.camera.it}, label={lst:dati}]{queries/dati.rq}
\end{enumerate}
